What We Eval in the Shadows

### 2021-09-09 paper/main.tex
More fixes

\begin{itemize}[---]
\item \emph{Function:} environments for the local variables of some function
  currently active on the call stack. Obtained by calling \k{parent.frame()} or
  \k{sys.frame()}.
\item \emph{Synthetic:} environments built from data structures such as lists,
  data.frames, or constructed explicitly with \k{new.env}, \k{list2env}, or
  \k{as.environment} or the empty environment.
\item \emph{Global:} environments in which scripts or interactive commands are
  evaluated.
\item \emph{Package:} environments of libraries.
\end{itemize}

@@

\begin{lstlisting}[title={\k{glue::glue_data}}, captionpos=b]
> flights[carrier=="DL" & year == 2014, mean(dep_delay), by=origin] |>
    glue_data("{origin} has average delay of {round(V1)} min")
# LGA has average delay of 11 min
# EWR has average delay of 15 min
# JFK has average delay of 12 min
\end{lstlisting}

@@

\begin{lstlisting}[H,caption={Unnecessary use of \eval},label=lst:unnecessary]
 PerformanceAnalytics::chart.QQPlot <- function (d="norm",dp,...) {
   q.f <- eval(parse(text=paste0("q",d)))
   z <- NULL
   eval(parse(text=paste0("z<-q.f(",dp,",...)")))
   ...
 }
\end{lstlisting}\medskip

@@

\begin{lstlisting}[H]
 q.f <- get(paste0("q",d))
 z <- q.f(dp, ...)
\end{lstlisting}

>>>>

\enlargethispage{2mm}
\begin{itemize}[---]
\item \emph{Function:} environments for the local variables of some function
  currently active on the call stack. Obtained by calling \k{parent.frame()} or
  \k{sys.frame()}.
\item \emph{Synthetic:} environments built from data structures such as lists,
  data.frames, or constructed explicitly with \k{new.env}, \k{list2env}, or
  \k{as.environment} or the empty environment.
\item \emph{Global:} environments in which scripts or interactive commands are
  evaluated.
\item \emph{Package:} environments of libraries.
\end{itemize}

@@

\enlargethispage{2mm}
\begin{lstlisting}[title={\k{glue::glue_data}}, captionpos=b]
> flights[carrier=="DL" & year == 2014, mean(dep_delay), by=origin] |>
    glue_data("{origin} has average delay of {round(V1)} min")
# LGA has average delay of 11 min
# EWR has average delay of 15 min
# JFK has average delay of 12 min
\end{lstlisting}

@@

\begin{lstlisting}[caption={Unnecessary use of \eval (\k{PerformanceAnalytics::chart.QQPlot})},label=lst:unnecessary]
function (d="norm", dp, ...) {
   q.f <- eval(parse(text=paste0("q", d)))
   z <- NULL
   eval(parse(text=paste0("z<-q.f(", dp, ", ...)")))
   ...
 }
\end{lstlisting}\medskip

@@

\begin{lstlisting}
 q.f <- get(paste0("q", d))
 z <- q.f(dp, ...)
\end{lstlisting}
